### 2024-05-28 Scripts/Manuscript/manuscript.Rmd
revised the entire text to the main article form. Added a new figure, removed some tables and analyses, appendiced some analyses.

---
title             : "The Impact of Measurement Practices and Measurement Error on Construct Validity and Replication Outcomes in Psychological Science"
shorttitle        : "Measurement Quality and Replicability"

author: 
  - name          : "Goos, C."
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Professor Cobbenhagenlaan 125, 5037 DB, Tilburg, The Netherlands"
    email         : "casgoos99@gmail.com"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Data curation"
      - "Formal Analysis"
      - "Investigation"
      - "Methodology"
      - "Visualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Nuijten, M.B."
    affiliation   : "1"
    role:
      - "Project Administration"
      - "Writing - Review & Editing"
      - "Supervision"

@@

  Enter author note here. Jelte/Marjan?

abstract: |
  Recently, the influence of measurement related issues on replicability has received more investigations. 
  In particular, studies have indicated that low reliability, and poor measurement reporting can negatively influence the replicability of an effect. 
  Building on this new line of research, this study assessed the influences of poor measurement reporting in replications from the Many Labs replication projects, and the original articles that the replications were based on, while publicly available data from the Many Labs replications was used to assess the reliability of the measures. 
  Here we show that while contrary to expectations reliability did not relate to replicability, the quality of measurement reporting in replications did relate. 
  For original articles the quality was indirectly related to replicability through the quality of measurement reporting in replications.
  These and other descriptive results indicate similarly to previous research that measurement details in both original research and replications are underreported.
  However, some of the issues in measurement reporting that were identified as most critical in this study differ from what has been stated in previous research.
  Measurement is a crucial part of almost all empirical research, it's details should tehrefore be transparently reported to enable critical evaluation and independent replication.
  Consequently, recommendations are given to researchers and replicators on the measurement practices that are  most crucial to improve on.. 
  Finally, directions are given for future research to further investigate the (causal) relationship between measurement practices and replicability.

keywords          : "reliability, measurement, measurement reporting, replicability, construct validity"
wordcount         : "234"

@@

\setcounter{topnumber}{3} <!-- max number of floats at top of page --> \setcounter{bottomnumber}{3} <!-- max number of floats at bottom of page --> \setcounter{totalnumber}{4} <!-- max number of floats on a page --> <!-- remember to use [htp] or [htpb] for placement -->

@@

For many years, methodologists and statisticians have raised concerns about the way that research practices [@cumming2014new; @wicherts2016degrees], reporting practices [@bakker2011mis; @nuijten2016prevalence], and publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science] may undermine the credibility of psychology's scientific claims. Replicability of a finding is seen as one crucial step in establishing its credibility [@nosek2022replicability]. In order to investigate the replicability of psychological science, the large scale Reproducibility Project: Psychology (RPP) was set-up [@osc2015estimating]. Replications of 100 published studies were performed using similar materials, procedures, and analyses, while using a new sample of participants for each study. They found however, that in many instances the results did no match those of the original studies. This lack of replicability of psychological findings led to the claim that psychology was facing a 'replication crisis' [@hughes2018psychology; @giner2019crisis].

As a response, the demand to verify the credibility of psychological findings through replications rose. In order to attempt replications of various psychological findings, numerous large scale projects were set-up [@klein2014investigating; @camerer2016evaluating; @camerer2018evaluating; @ebersole2016many; @ebersole2020many; @klein2018many; @klein2022many]. Among these were the Many Labs projects, which operated similarly to the RPP, with the additional feature that each original article was replicated multiple times across different labs in various locations around the world. The results from these replication projects generally showed smaller effects than those reported in the original studies. Similarly, effects that had reached statistical significance in the original no longer did across the aggregate results of its replications.

Several explanations for this discrepancy between original and replication findings have been suggested and investigated, with many being centred around the concept of Questionable Research Practices [QRPs, @john2012measuring]. QRPs are practices, which either misrepresent or omit essential methodological information that is needed to evaluate the research. Without this information, a reader will not know whether the result was in line with the author's expectation or simply the result of repeated trial and error until a suitable result was found [@simmons2011false]. Consequently, much of the discourse and the subsequent proposed solutions have been centred around preventing these QRPs through increased transparency in scientific reporting.

However, many researchers have also raised concerns that other factors, such as low power [@stanley2018what], lack of strong theoretical foundations [@eronen2021theory], and validity [@finkel2017replicability], which have not been given as much attention, are just as if not more responsible for the lack of successful replications found in psychology. Another factor which has gained more traction recently are measurement related issues' impact on replicability. In particular, studies shown that measurement error and questionable measurement practices may impact replicability [@stanley2014expectations; @shaw2020measurement; @flake2017construct; @flake2020measurement].

Measurement in psychological science is defined in large part by one overarching issue: the psychological constructs of interest, such as affective state and intelligence, cannot be measured directly [@flake2017construct]. As a result, psychologists face two primary challenges in the use of measurement: First of all, the measure has to assess the construct it intends to measure, even though it can only do so indirectly. Secondly, because the measurement is indirect, it also comes with some degree of error surrounding its assessment of the construct. The first issue relates to the concept of validity, and specifically construct validity. Validity refers to the overall extent to which a measure measures what it is supposed to [@borsboom2004concept], while construct validity specifically refers to the substantial relation between the item scores on a psychological measure and the psychological construct it intends to measure. In order for indirect assessment of psychological constructs to be a viable approach, the measure needs to have construct validity [@cook2002experimental]. The second issue relates to the concept of measurement error and reliability. Measurement error indicates the amount of variation in item scores that is the result of the used measures inaccuracies, and not due to differences in the underlying psychological construct of interest.

@stanley2014expectations demonstrated, using a simulation study, the impact measurement error has on attempts to verify or falsify findings. Scalar item data was generated based on levels of sampling error and score-reliability, as the inverse of measurement error, that mimicked what is standard in psychological research, to ensure that the resulting degree of error was representative. The results indicated that measurement error caused observed effects found in replication research to vary heavily.

Even when ignoring reliability, a measurement's content and implementation still need to validly capture what it intends to measure. Questionable Measurement Practices (QMPs) are practices that decrease the availability of information needed to evaluate a measurement's validity, and have been coined as a conjugate term to QRPs. They range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of measure and procedure of any sourced measures [@flake2020measurement]. When this information is missing, it becomes difficult to establish that original and replication are measuring the same construct(s), which has detrimental consequences for direct replication attempts.

This study aims to investigate the influence of both measurement error and QMPs on replicability, using data and reports from the large scale Many Labs replication projects. One goal is to expand the research by [@stanley2014expectations] with a practical example. Whereas they obtained their findings using a simulation study, this study investigated the scope of their findings on data from real replications. QMPs in the context of replication research were already investigated by [@flake2022construct]. However, the investigations remained mostly descriptive. This study additionally aims to expand upon the findings of [@flake2022construct] through the use of a new set of replication data, and by exploratively investigating the relation between QMPs and replicability.

## Measurement Error
As a first step the state of measurement error in original and replication research in psychology is investigated, to assess the scope of @stanley2014expectations's findings in practice:

-   RQ1a. What is the degree of score reliability in replications of psychological research?

-   RQ1b. What is the degree of score reliability in original psychological research?

Since direct replications intend to investigate effects in nearly identical scenarios with nearly identical measures as the original study, it is expected that measurement errors are as present in the replication research looked at in this study as in the accompanying original psychological research.

@@

While reliability estimates are generally considered a measure specific feature, this is false. They are context dependent, and as a result the estimates of an effect can differ across contexts [@cho2015cronbach; @pauly2018resampling]. With large enough differences across contexts, the effect estimates between different replication attempts could deviate from each other beyond direct comparison. To investigate this potential problem, the variation in score reliability is assessed for each measure when used across a set of replications of the same effect in contexts.

@@

Even though reliability estimates are context dependent, sufficient protocol structure can counteract the variance in reliability estimates. An example of the standardizing impact a structured protocol can have on reducing variability within an effect can be found in investigations into the closely related issue of heterogeneity [@patacchini2007unobserved]. Heterogeneity refers to the true variation in the true effect size due to minor but key differences in context, environment, and procedure. Heterogeneity is yet another proposed explanation for failed replications. This concern even prompted a Many Labs centered around the testing of heterogeneity in replications [@klein2018many]. However analyses from this Many Labs, and @olsson2020heterogeneity showed little empirical evidence for widespread heterogeneity in effects among replications. These findings demonstrate that it is possible to reduce variability as the result of context using structured protocols, as was done in the Many Labs projects this study analyzed.

@@

This study investigated whether there is something in the measures used for replicated findings that sets them apart from those used for non-replicated findings. One of the elements this study looked at is the reliability of replicated studies compared to the non-replicated studies, thus extending the research by @stanley2014expectations on the relationship between reliability and replicability with data from real life replication projects.

@@

Greater score-reliability means greater consistency in estimation as variance around the estimate of the true effect is decreased. Consequently measures across different occasions, including between original and replication, should also become more consistent [@nunnally1994assessment]. When original and replication research share consistent result, and as long as the studied effect is true, then on average their statistical conclusions should converge.

@@

## Questionable Measurement Practices
A measure not only needs to be reliable, it should also in its design and implementation adequately capture what it intends to measure [@flake2020measurement]. Any scientific report should therefore clearly motivate the use of measure and procedure. When these aspects are not clearly reported on, the validity of measurement remains uncertain. Therefore, the other tests of this paper focused on the reporting aspects of measurement, assessed through QMPs.

This study sought first of all to conceptually replicate some of the findings of @flake2022construct about QMP reporting in the RPP within the Many Labs replication projects.

@@

@flake2022construct coded the presence of a series of QMPs in the replication report in both the replication protocols of each replication in the RPP, as well as the original articles the replications were based on. They found that not only are QMPs common in psychological research, they can be even more common in replications reports. However, the reporting of the Many Labs projects differ from the RPP data used in @flake2022construct. The structured and preregistered protocols used for the Many Labs projects were hypothesized to lead to consistent reporting of important measurement details, and as a result contain less QMPs.

@@

QMPs may obscure relevant information needed to evaluate the use of measurement in a study. If the replication used the measure differently from the original, the replication may no longer be a direct replication. As a result, there is additional deviation in the estimate of the effect from the original, due to differences in measurement. Establishing a link between QMPs and non-replicability should confirm suspicions of their detrimental effects on replications [@flake2017construct; @flake2020measurement; @flake2022construct].

@@

Fewer QMPs means that measurement decisions in a report are transparent with the number arbitrary methodological decisions being limited as well. Fewer arbitrary decisions means less ways that a replicator can deviate from the original's intended effect. One of the Many Labs projects even touched on this concept [@ebersole2020many]. In this project, peer-review of replication protocols by original authors was used to ensure that approved methods were used. Additionally, it has been observed that authors who promote greater transparency in their work, have on average stronger evidence for their hypotheses [@wicherts2011willingness]. Finally, the results shown in @protzko2020high illustrate that when original studies are transparent, preregistered, and have adequate sample size, subsequent replication attempts find nearly the same effect size as the original. All of these findings point towards a positive relation between successful replication and various types of good research practices. A similar relation is expected for good measurement practices.

-   H5. QMPs in replication research are negatively associated with replication of an original finding.

This study additionally aims to see if the relation between QMPs and replicability can be traced back to original article QMPs. When essential information on a measure is not available in an original article, it may be difficult to know the specifics of that measure to report for a replication. Therefore this study also investigates the relation between original QMPs and replication QMPs.

@@

If the relationship exists, it is expected that questionable measurement practices in an original paper might cause a spill-over effect of QMPs into the replication. @flake2022construct found that QMPs linked to issues for replicators in recreating the measurement to closely match the measurement in the original. As a result, there was a lack of measurement related information in both replication reports, and original articles. Additionally, investigations by @shaw2020measurement have shown that more validity evidence in an original article is associated with better psychometric properties in the replication sample. Based on these arguments, QMPs are expected to be associated across original and replication studies.

@@

@@

Data collection, coding protocol, and planned analyses were all preregistered. The preregistration and supplementary materials can be found on this article's OSF page: <https://osf.io/9r8yt/>. Any deviations from the preregistration are explicitly mentioned in the text. This manuscript was created in Rstudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency. All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication.git>.

@@

The data used for the analyses in this study consists of three main sources: replication datasets, preregistered replication protocols, and original study articles. The data came from the Many Labs series of studies. In particular, data from Many Labs 1, 2, 3, & 5 was used [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many]. Data from Many Labs 4 [@klein2022many] was not part of the sample, as there was no publicly available protocol which contains the information needed to code QMPs. Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study's focus on scale and item measures.

The total number of identified psychological findings for which replication was attempted across the four included Many Labs projects amounts to a total of `r sum(table(coded_data_replications$many_labs_version, coded_data_replications$appearance)[,1])`. Each finding was tested across several labs, and was related to a finding from an original study, the combination of all these studies and their associated information formed a replication set. For each research finding, any primary measures assessing a unique variable were taken to form the key unit of analysis. Here primary measures refers to measures assessing variables included in the primary test of the replication. This was done to ensure that the analyses could link directly to the replicability of a study. Acquiescence bias checks, manipulation checks, measures used for pilot testing, and measures added for exploratory analyses in replication studies were not included. The result was a total sample size of `r nrow(coded_data_replications)` measures used in both original and replication research[^1]. Table \@ref(tab:ManyLabsDescriptivesTable) shows further descriptive information about the data for each Many Labs Project.

[^1]: Initially the original articles were coded to have 3 more measures than the replication protocols. However, these measures were all related to the moral foundations questionnaire, and could be altered from representing five different moral foundations to the two overarching categories of individualizing and binding foundations found described in the replication protocol without much issue or loss of information.

```{r ManyLabsDescriptivesTable, warning = FALSE}
# construct the Many Labs descriptives table to be printed
many_labs_descriptives_table <- data.frame("Many Labs Version" = c("1", "2", "3", "5", "Total"),
                                      "N ML Projects" = c(table(coded_data_replications$many_labs_version, coded_data_replications$appearance)[,1], sum(table(coded_data_replications$many_labs_version, coded_data_replications$appearance)[,1])),
                                      "N Primary Measures" = c(table(coded_data_replications$many_labs_version), nrow(coded_data_replications)), 
                                      "Replication Total N" = c(apa_num(mean(coded_data_replications$N[coded_data_replications$many_labs_version == "1"], na.rm = TRUE), digits = 0),
apa_num(mean(coded_data_replications$N[coded_data_replications$many_labs_version == "2"], na.rm = TRUE), digits = 0),
apa_num(mean(coded_data_replications$N[coded_data_replications$many_labs_version == "3"], na.rm = TRUE), digits = 0),
apa_num(mean(coded_data_replications$N[coded_data_replications$many_labs_version == "5"], na.rm = TRUE), digits = 0), apa_num(mean(coded_data_replications$N, na.rm = TRUE), digits = 0)), 
"Replication Total IQR" = c(apa_num(IQR(coded_data_replications$N[coded_data_replications$many_labs_version == "1"], na.rm = TRUE), digits = 0),
apa_num(IQR(coded_data_replications$N[coded_data_replications$many_labs_version == "2"], na.rm = TRUE), digits = 0),
apa_num(IQR(coded_data_replications$N[coded_data_replications$many_labs_version == "3"], na.rm = TRUE), digits = 0),
apa_num(IQR(coded_data_replications$N[coded_data_replications$many_labs_version == "5"], na.rm = TRUE), digits = 0), apa_num(IQR(coded_data_replications$N, na.rm = TRUE), digits = 0)),
"Original Total N" = c(apa_num(mean(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "1"], na.rm = TRUE), digits = 0),
apa_num(mean(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "2"], na.rm = TRUE), digits = 0),
apa_num(mean(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "3"], na.rm = TRUE), digits = 0),
apa_num(mean(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "5"], na.rm = TRUE), digits = 0), apa_num(mean(coded_data_original_shortened$N, na.rm = TRUE), digits = 0)),
"Original Total IQR" = c(apa_num(IQR(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "1"], na.rm = TRUE), digits = 0),
apa_num(IQR(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "2"], na.rm = TRUE), digits = 0),
apa_num(IQR(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "3"], na.rm = TRUE), digits = 0),
apa_num(IQR(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "5"], na.rm = TRUE), digits = 0), apa_num(IQR(coded_data_original_shortened$N, na.rm = TRUE), digits = 0)))

# Adding column names to the table for readability
colnames(many_labs_descriptives_table) <- c("ML Version", "N Projects", "N measures$^a$", "Rep. N", "Rep. IQR", "Org. N", "Org. IQR")

### failed table
# colnames(many_labs_descriptives_table) <- c("Version", "Projects", "Measures", "Total N", "Total IQR", "Total N", "Total IQR")

# c("", "N ML", "N Primary", "Replication", "Replication", "Original", "Original")

# kableExtra::kbl(many_labs_descriptives_table, align = c("l", "r", "r", "r", "r", "r", "r"), escape = FALSE, placement = "htp", row.names = FALSE) %>%
#   kableExtra::kable_classic( full_width = FALSE) %>%
#   kableExtra::add_header_above(c("Many Labs" = 1, "N ML" = 1, "N Primary" = 1, "Replication" = 1, "Replication" = 1, "Original" = 1, "Original" = 1), line = FALSE) %>% 
#   kableExtra::row_spec(4, extra_latex_after = "\\cmidrule(l{3pt}r{3pt}){2-5}")

# midrule wouldn't add ):<

# print the table in apa formatting
apa_table(
  many_labs_descriptives_table, align = c("l", "r", "r", "r", "r", "r", "r"), escape = FALSE, placement = "htp", midrules = 4, caption = "General Descriptives of the Many Labs Projects"
  , note = "$^a$ refers only to the number of identified primary measures, which this study is concerned with. Rep. = Replicaiton, Org. = Original., N = total number of, IQR = Interquartile range.")
```

@@

The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. Both the replication protocols and replication datasets were scanned through to ensure that the planned analyses were feasible. However, no coding or analysis of either of them had taken place before the analyses were preregistered. Further details on the search strategy can be found in the data_search_details.pdf supplementary materials.

@@

The replication datasets refer to the data of each of the replication attempts for each of the original psychological effects undertaken as part of a Many Labs study. These publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio [@R-Rstudio]. When available, codebooks, analysis scripts and study materials were used to identify the specific data for each measure. The variables associated with each relevant measure were extracted into their own dataframe containing the data from all studies in one replication set. These dataframes together formed the dataset used for the analyses.

>>>>

---
title             : "An Empirical Assessment of Reliable and Valid Measurement as a Prerequisite for Informative Replications"
shorttitle        : "Measurement Quality and Informative Replications"

author: 
  - name          : "Goos, C."
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Professor Cobbenhagenlaan 125, 5037 DB, Tilburg, The Netherlands"
    email         : "casgoos99@gmail.com"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Data curation"
      - "Formal Analysis"
      - "Investigation"
      - "Methodology"
      - "Project Administration"
      - "Software"
      - "Visualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Bakker, M."
    affiliation   : "1"
    role:
      - "Supervision"
      - "Writing - Review & Editing"
  - name          : "Wicherts, J.M."
    affiliation   : "1"
    role:
      - "Supervision"
      - "Writing - Review & Editing"
  - name          : "Nuijten, M.B."
    affiliation   : "1"
    role:
      - "Conceptualization"
      - "Project Administration"
      - "Supervision"
      - "Validation"
      - "Writing - Review & Editing"

@@

abstract: |
  Psychological science has been facing threats to the credibility of its findings, particularly due to the lack of replicability of findings.
  Recently, there has been increasing attention towards the impact that features of psychological measurement, specifically reliability and measurement reporting, has on replicability.
  In this article, we assessed the reliability and measurement reporting within the Many Labs replications and the original studies they were based on. 
  We then empirically investigated the associations of replicability with reliability and measurement reporting.
  The results indicated that not all measures were sufficiently reliable across contexts. 
  Additionally, reliability and validity evidence was rarely reported. 
  Finally, incompleteness in measurement reporting was associated with lower replicability of the findings tested with that measure.
  The results not only indicate potential issues in reliability and validity of measures, but also that incomplete measurement reporting may negatively affect replicability. 
  These findings illustrate the importance of reliable measurement, and complete measurement reporting for establishing credible findings. 
  The article ends with suggestions to improve measurement reporting. 
  We further suggest that the reported measurement information should be evaluated when  researchers decide what studies to replicate.

keywords          : "reliability, validity, measurement, measurement reporting, replicability, credibilitys"
wordcount         : "182"

@@

\setcounter{topnumber}{3} <!-- max number of floats at top of page -->

\setcounter{bottomnumber}{3} <!-- max number of floats at bottom of page -->

\setcounter{totalnumber}{4} <!-- max number of floats on a page -->

<!-- remember to use [htp] or [htpb] for placement -->

@@

For solid scientific progress in psychology, we need to be able to rely on previous findings - findings should be credible. Unfortunately, psychology seems to face several threats to the credibility of its findings. In this article, we investigate how the credibility of psychological findings may be affected by problems in psychological measurement, and in turn, how those problems may affect successful replication.

### Credibility & Replicability

A prerequisite for a credible finding is that it is replicable [@vazire2022CredibilityReplicabilityImproving]. This means that the observed effect should be comparable across the original study and subsequent replications as long as the differences between them are believed to be of little relevance to the effect [@nosek2022replicability].

In practice, effects deviate substantially between original and replication research. In 2015, the Replication Project: Psychology (RPP) attempted replications of 100 research findings in psychology, they observed a substantial discrepancy between the replication findings as compared to the original findings [@osc2015estimating]. Similarly, the Many Labs projects replicated the effects reported in original articles across different labs in various locations around the world [@klein2014investigating; @camerer2016evaluating; @camerer2018evaluating; @ebersole2016many; @ebersole2020many; @klein2018many; @klein2022many]. There it was observed that effects were on average smaller in replication compared to original research. Furthermore, there was variation within the estimates of the effect between different lab locations.

In response to this string of failed replications, there was widespread alarm regarding the credibility and robustness of findings in psychological science [@hughes2018psychology; @giner2019crisis]. Simultaneously researchers sought to explain this discrepancy. The factors that have been proposed include, questionable research practices [@simmons2011false; @john2012measuring; @cumming2014new; @wicherts2016degrees], questionable reporting practices [@bakker2011mis; @nuijten2016prevalence], and biased publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science]. A factor that has gained more traction recently is the impact of measurement-related challenges on replicability.

### Credibility & Measurement

Measurement in psychological science is characterized in large part by one overarching issue: psychological constructs, such as affective state or intelligence, can usually not be measured directly [@flake2017construct]. As a result, psychologists face two primary challenges in the use of measurement: First of all, because the measurement is indirect, it also comes with some degree of random error surrounding its assessment. Secondly, the responses on the measure have to relate to the psychological construct(s) of interest, but as the construct is not directly observable, this is difficult to assess.

The first issue relates to the concept of reliability, which gives an indication of how consistent the responses on a measurement are. Reliability is a critical first step to obtaining credible findings. Because if the scores on a measure are not consistent with themselves, it is unlikely that any effect associated with the measure can be consistently established.

The second issue relates to the concept of validity, and specifically construct validity. Validity in measurement refers to the overall extent to which a measure measures what it is supposed to [@borsboom2004concept], while construct validity refers to the substantial relation between the scores on a measure and the related psychological construct. A researcher cannot assume to have found a credible psychological effect, if the measures do not relate to a psychological construct [@cook2002experimental].

### Replicability & Measurement

Whereas both reliable and valid measurement and replicability are important elements that independently contribute to the overall credibility of a finding, there may also be a relation between the two. Indeed, recent studies have illustrated that both the reliability of the measure [@stanley2014expectations] and the reporting of the measure [@shaw2020measurement; @flake2017construct; @flake2020measurement] can affect the credibility of psychological studies, and in turn explain the lack of replication success. This study aims to investigate the influence of both measurement reliability and measurement reporting on replicability, using data and reports from the large scale Many Labs replication projects.

### Many Labs Sample Description

In the Many Labs projects each effect was directly replicated across multiple lab locations over the world. As a result the data obtained from these measures allows us to say something about the variability in these measures across different contexts. Another important aspect of the Many Labs projects is that the measurement was preregistered and documented in structured protocols that were used to instruct all the participating labs. We believe that these represent some of the best practices in measurement usage in psychology. Therefore, any problems with the measurement and its reporting encountered in this sample would not bode well for measurement in the rest of psychology.

## Existing Research

### Reliability

While reliability is generally considered a measure specific feature, this is false. The reliability of a measure is context dependent [@cho2015cronbach; @pauly2018resampling], and as a result so are the scores obtained with that measure. The contextual variations in the measurement scores could explain the discrepancy between effects in original and replication research, as well as within replications of the same original effect. Besides random variation due the sampling error, the variations can also reflect true variation in reliability, also known as reliability heterogeneity [@vacha-haase1998ReliabilityGeneralizationExploring]. For instance, measures are known to generally show lower reliability in more homogeneous samples as compared to heterogeneous samples [@pike1998reliability].

However, even when reliability is the same across studies, reliability can still cause estimates of the same effect to vary significantly. @stanley2014expectations simulated data of items on a scale based on levels of sampling error and reliability similar to what is standard in psychological research. The results indicated that measurement error due to imperfect reliability caused variation in the observed effect sizes in the simulated replications, on top of sampling error. The added variation was substantial enough to cause replications of a positive small effect to observe anywhere between a medium negative effect and a large positive effect [@stanley2014expectations]. This implies that studies using unreliable measures have a lower probability to be successfully replicated, even if the underlying effect is true and the measurement is equally reliable between original and replication.

### Measurement Reporting

Despite the importance of having reliable and valid measures, research has shown that Questionable Measurement Practices (QMPs) in reporting are not uncommon. QMPs are practices that raise doubts about a measurement's validity [@flake2020measurement], and have been coined as a conjugate term to Questionable Research Practices [QRPs, @john2012measuring]. QMPs range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of measure and procedure of any sourced measures [@flake2020measurement].

@flake2020measurement identified the main questions that the article should answer in relation to the measurement used: the definition of the construct, how the measure was selected, how the measure was operationalized, how the measure was quantified, whether it was modified or not and why, and the reasons and details of creating a measure if applicable. The questions together form the basis of the information that a researcher should present in order to be transparent and promote a more cumulative psychological science.

@flake2022construct documented QMPs among 100 replications and their respective original articles from the RPP [@osc2015estimating]. They coded the number of measures, the number of items in the measure, and the information that was reported describing the measure and providing evidence justifying its use. Besides limited reporting of validity and reliability evidence for the coded measures, @flake2022construct found that several of the measures in the RPP did not report the number of items, the response format, or the scoring of the scale. Furthermore, only 8 of the 40 translated scales contained validity evidence for the translated version of the scale. Measures were similarly modified between original and replication in other ways without evidence showing that the modification did not invalidate the measurement.

Further findings by @flake2022construct and others [@flake2017construct; @shaw2020measurement] illustrated how QMPs create challenges for replicating researchers. Replicating researchers will need detailed information on the measurement in the original study to reconstruct it. If the measure is not reconstructed exactly, original and replication may be measuring different construct(s). In that case, different effect size estimates in original compared to replication research may very well be due to the fact that the effects are between different constructs, and not because the effect was not robust to sampling error.

### Research Contribution

Our study aimed to investigate the influence of both measurement reliability and measurement reporting on replicability, using data and reports from the large scale Many Labs replication projects. Firstly, this study expands on the research by @stanley2014expectations using an empirical example. Our goal was to see whether reliability was related to replication success on real life replication data. In practical terms, we investigated whether or not replicated studies differed in their reliability scores from non-replicated studies. In their study @stanley2014expectations assumed reliability to be constant across studies, which we know to be an oversimplification. Therefore, to add further context to relation between reliability and replication, this study also investigated the variation in reliability as observed across separate measurement occasions.

Furthermore, this research conceptually replicates the study by @flake2022construct on QMPs in replications and original research, now in the context of the Many Labs projects. We then expand on @flake2022construct by exploring associations between QMPs and the replicability of psychological findings.

## Research Questions & Hypotheses:

### Reliability

Measurement reliability varies across contexts. It is crucial for evaluating replications that differences between replication and original are understood and accounted for.

-   RQ1a. What is the degree of score reliability in replications of psychological research?
-   RQ1b. What is the degree of score reliability in original psychological research?

The Many Labs studies were intended as direct replications. In direct replications, any deviations from the original research are believed to be irrelevant for testing the same effect as the original study [@nosek2022replicability]. In that case, the reliability of measurements in replications should also not deviate systematically from the original research.

@@

Reliability has the potential to vary not only between replication and original research, but also within replications of the same effect [@vacha-haase1998ReliabilityGeneralizationExploring].

@@

Heterogeneity could be a major contributor to this variation. However for effect sizes there is little empirical evidence of widespread heterogeneity among the Many Labs replications [@klein2018many; @olsson2020heterogeneity]. The same is expected to hold true for the heterogeneity in reliability coefficients among the Many Labs replications.

@@

In order to see if reliability has an impact on replication attempts, we investigated whether or not successfully replicated studies differ in the reliability of their measures as compared to non-replicated studies.

@@

Greater reliability means the variance around the estimate of the true effect is decreased [@nunnally1994assessment]. Assuming that the true effect is not null, then the statistical conclusions tested with reliable measures are be more likely to converge to significance.

@@

### Measurement Reporting

With respect to measurement reporting, this study first of all aims to conceptually replicate some of the findings of @flake2022construct.

@@

@flake2022construct found that QMPs were overall more common in the RPP replications as compared to the original research. We did not hypothesize this same effect to hold for the Many Labs sample, because of the use of structured protocols documenting the measurement.

@@

Differences in measurement resulting from QMPs have been suspected to cause replication and original effects to deviate [@flake2022construct]. Investigating the link between QMPs and non-replicability should put this suspicion to the test.

@@

A reduction in QMPs corresponds to greater transparency in reporting of measurement. Research on other transparency related practices have shown that these are associated with more robust estimates of effects [@wicherts2011willingness; @protzko2020high]. We expect a similar effect for QMPs.

-   H5. QMPs in replication research are negatively associated with successful replication of an original finding.

One of the reasons measurement in replication may deviate is because original articles did not report all the necessary information needed to mimic the original measurement. In this way a lack of information may carry over from the original article to the replication.

@@

Previous research by @flake2022construct has shown that QMPs in original articles cause issues for recreating measurements for replication research. Additionally, @shaw2020measurement found similar spill-over effects for validity. Based on these findings, QMPs in original research were expected to be associated with QMPs in replication research.

@@

# Disclosures

### Preregistration

Data collection, coding protocol, and planned analyses were all preregistered. The preregistration and supplementary materials can be found on this article's OSF page: <https://osf.io/9r8yt/>. Any deviations from the preregistration are explicitly mentioned in the text.

### Data, materials, and online resources

This manuscript was created in Rstudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency. All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> & <https://osf.io/9r8yt/>.

### Reporting

We report how we determined all data exclusions, all manipulations, and all measures in the study. Our sample size was based on the number of usable studies in the Many Labs studies.

### Ethical Approval

This research was approved by the Tilburg University School of Social and Behavioral Sciences Ethical Review Board.

@@

@@

### Data Source

The data used for the analyses in this study consists of three main sources: replication datasets, preregistered replication protocols, and original study articles. The data came from the Many Labs series of studies. In particular, data from Many Labs 1, 2, 3, & 5 was used [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many]. Data from Many Labs 4 [@klein2022many] was not part of the sample, as there was no publicly available protocol which contains the information needed to code QMPs. Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study's focus on item-based measures.

### Unit of analysis

Measures were identified using the preregistered replication protocols. Acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses were not included. The result was a total sample size of `r nrow(coded_data_replications)` measures used in both original and replication research[^1].

[^1]: Initially the original articles contained 3 more measures than the replication protocols. This difference was due to the way that the moral foundations questionnaire was framed in the original articles compared to in the original article. In the original article it was framed as measuring five different moral foundations, while in the replication protocol the measure was described as measuring the two overarching categories that were used to test the main effect in the original and replication research. The measurement information reported was comparable across all five categories, and thus it was deemed that the measurement could be reduced to reflect two overarching categories to make comparison between original and replication easier.

@@

The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. Both the replication protocols and replication datasets were scanned through to ensure that the planned analyses were feasible. However, no coding or analysis of either of them had taken place before the analyses were preregistered. Further details on the search strategy can be found in the [coding protocol information file](../../SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd) supplementary materials.

@@

The replication datasets refer to the publicly available datasets containing the data obtained from all of the labs that took part in one of the Many Labs studies. These datasets were accessed through their OSF page. For the analyses, the scores on the items of an identified measure were identified and extracted. When scores could not be clearly identified, any available codebooks, analysis scripts or study materials were used to identify the relevant scores.

In order to be considered suitable for the planned analyses on calculated reliabilities, the measure had to be a scale consisting of multiple items. If cleaned data was available this was chosen over raw data, to ensure that variables were coded as intended (e.g. no reverse-coded items). Pilot data were omitted from the analyses entirely. These criteria resulted in suitable item score data from `r apa_num(length(unique(data_h3_multiple$g)), numerals = FALSE)` replication sets spread across on average `r apa_num(mean(table(data_h3_multiple$g)), digits = 0)` lab locations for the analyses of hypotheses 2 & 3.
